On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-04-06 problem_statement.tex
full review of the formalization section

@@

generality of the results since they takle a specific step (and not the first) of the engineering of system.

@@

there is no sucha theory).

@@

is verified. As an example, for the formal security verification of the system

@@

improves issues when discovered, there is no agreement on which should be

@@

\subsection{Sicurezza: Safety and Security}\label{sec:sicurezza}

@@

>>>>

Before going into the details of the literature review, we show that the lack
of agreement on what security is can actually be found in the literature, and
can be categorized with respect to the method of enquiry.  In the following, we
provide three examples based on the categorization provided by Sextus Empiricus
in \autocite{Empiricus1990Pyrrhonism}, since it appear to us to be
comprehensive. ``The natural result of any investigation is that the
investigators either discover the object of search or deny that it is
discoverable and confess it to be in-apprehensible or persist in their search.
[\ldots] This is probably why''\autocite{Empiricus1990Pyrrhonism}: 
\begin{itemize}
	\item The \emph{dogmatists} ``have claimed to have discovered the truth''
		\begin{itemize}
			\item Wikipedia defines cybersecurity in
				\autocite{wiki-cybersecurity} as the protection
				of computer systems and networks from the theft
				of or damage to their hardware, software, or
				electronic data, as well as from the disruption
				or misdirection of the services they provide.
		\end{itemize}
	\item The \emph{academics} ``have asserted that it cannot be apprehended''
		\begin{itemize}
			\item Eugene H. Spafford, Professor at Purdue
				University, defines cybersecurity as follow.
				``The only truly secure system is one that is
				powered off, cast in a block of concrete and
				sealed in a lead-lined room with armed guards —
				and even then I have my doubts.''
				\autocite{Spafford2019Quotes}
		\end{itemize}
	\item The \emph{skeptics} ``go on inquiring''
		\begin{itemize}
			\item Cormac Herley reaches the conclusion that
				cybersecurity has no definition. ``There is an
				inherent asymmetry in computer security: things
				can be declared insecure by observation, but
				not the reverse. There is no test that allows
				us to declare an arbitrary system or technique
				secure. This implies that claims of necessary
				conditions for security are unfalsifiable. ''
				\autocite{Herley2016unfalsifiability}. Therefore, we propose our investigation.
		\end{itemize}
\end{itemize}

@@

the generality of the results since they takle a specific step (and not the first) of the engineering process (of system).

@@

there is no such a theory).

@@

is verified. More specifically, for the formal security verification of the system

@@

improves the issues we discussed, there is no agreement on which should be

@@

\subsection{Terminology: Safety or Security}\label{sec:sicurezza}

@@

Either a valid security hypothesis can be formulated based on one or more of
the concepts reviewed (and depicted in Figure~\ref{fig:safety-security}) or it
can't.  Since, in the next Section, we will define our security hypothesis (on
top of which we'll deveop a security theory) on those terms, if the second case
is true we will not formulate a valid security theory. However, while we want
to highlight that the incompleteness of this review may be a potential issue;
on the other hand, due to the nature of a literature review, it seems to us
that only an inductive approach can be used and then any literature review will
be incomplete.  If the first case applies, in one of those terms one shall find
a valid ground on top of which formulate a security hypothesis (assuming that a
valid security hypothesis exists).

Our literature review shows that most of the definitions relates insecurity to
dis-honesty (also called maliciousness or adversarial) of an agent (often
called adversary or attacker).  If those correlation are important for the
insecurity of systems, it is plausible that they are important for the opposite
concept, security.  Therefore, we define the following hypothesis.
\begin{hypothesis}{\bf Security as Honesty and Insecurity as Dishonesty --}
	\begin{itemize}
		\item a closed system can be considered \emph{secure} if there
			is no dishonest agent
		\item a closed system can be considered \emph{insecure} if
			there is a dishonest agent 
	\end{itemize}
	where an agent is any virtual or physical entity of the system or using
	the system (e.g. a device, a software, or a human being) and dishonesty
	is not necessarily related to malicious motivation but also to
	incompetence or lack of skills.
\end{hypothesis}
As in the Dolev-Yao theory, we may correlate ``being dishonest'' to ``not
following the intended behavior/rules''.  In the case of a generic system, a
dishonest agent is therefore, any agent that doesn't follow the intended
behavior (or functionality or logic) of the system.  Given the generality of
the definition, and its high level of abstraction, we may
conclude that the hypothesis seems evident. For example, a software can be
considered an agent of the system and whenever it has a bug, it can be
exploited causing an Incident. However, this hypothesis has lead to the
un-testable conclusion that the dishonest behaviors of agents cannot be defined
in general (e.g. due to the heterogeneity of agents and systems) 
and that huge repository of dishonest behaviors should be kept as
definition, such as CWE\autocite{MITRE2020CWEresearch}, CVE\autocite{CVE},
CAPEC\autocite{MITRE2020CAPEC}, NVD\autocite{NIST2020NVD} and many many other;
or that dishonesty of an agent with respect to a security protocol should be
defined as a number of predefined actions as in
\autocite{Turuani2006clatse,Basin2005ofmc,Armando2016satmc,Rocchetto2017interpolation}
(to name a few).

We now proceed with a more detailed analysis of the terms
and with the re-formulation of the security hypothesis.

### 2020-04-06 theory.tex
full review of the formalization section

If we consider \autocite{Empiricus1990Pyrrhonism}, the author applies a
``logical criterion'' to an agent, for instance a man, for instance a device in
a system (or a system) as in \autocite{Santaca2016abf}.  The instrument identified is sense
perception, because a man is considered as example, but we can abstract from the
concept of instrument and consider any received information, where information is
considered as in \autocite{Hintikka1993Information}; which can be
summarized by the following axiom: ``Information is specified by specifying
which alternatives concerning the reality it admits and which alternatives
excludes''. This means, for our argument, that considering a propositional
variable, which admits the two alternatives True/False, its information is
defined as Believed to be True/False and not Believed to be the opposite. 
%Similarly, when reasoning on a
%mereotopological region w.r.t. the RCC (e.g. RCC3 admits two regions to be
%equal, disjoint, or overlapping) information on this region should exclude
%some of the alternatives. 
Finally, in \autocite{Empiricus1990Pyrrhonism}
the author states that the logical criterium can be judged according to a frame of reference.
For our argument, as in \autocite{Santaca2016abf}, we define this concept
as Knowledge (or Facts); where knowledge is defined, as in \autocite{Steup2020epistemology}, as
a set of proposition known by an agent, such that: (i) knowledge requires belief,
(ii) knowledge require truth, (iii) knowledge must be \emph{properly justified}.

>>>>

\fix{mr}{
\Paragraph{Methodology}
We now conclude this section by detailign the line of reasoning we want to
apply to our investigation.
The epistemologic concept of Knowledge can be equated to the
concept of Truth.  Anything that is known is, therefore, also true. It is also
believed that Knowledge, defined as we did, is supposed to be inapprehensible.
In contrast, Beliefs are potentially true and leads new hypothesis. Due to the
structure of deductive reasoning we can only start from hypothesis and test the
deductive conclusions on the reality. Whatever a scientific-security-theory is,
it must be defined starting from hypothesis.  A sound reasoning must lead to
conclusion that shall be tested on a real system. Thefore, only at the end of
the reasoning we will be able to test, and judge, the quality of the theory
itself. The identification of hypothesis should start from probably true
beliefs (which means from Information), and then from the state of the art.
Instead of having a ``related work'' section, we review and cite the literature
throughout the paper.
If we consider \autocite{Empiricus1990Pyrrhonism}, the author applies a
``logical criterion'' to an agent, for instance a man, for instance a device in
a system (or a system) as in \autocite{Santaca2016abf}.  The instrument identified is sense
perception, because a man is considered as example, but we can abstract from the
concept of instrument and consider any received information, where information is
considered as in \autocite{Hintikka1993Information}; which can be
summarized by the following axiom: ``Information is specified by specifying
which alternatives concerning the reality it admits and which alternatives
excludes''. This means, for our argument, that considering a propositional
variable, which admits the two alternatives True/False, its information is
defined as Believed to be True/False and not Believed to be the opposite. 
%Similarly, when reasoning on a
%mereotopological region w.r.t. the RCC (e.g. RCC3 admits two regions to be
%equal, disjoint, or overlapping) information on this region should exclude
%some of the alternatives. 
Finally, in \autocite{Empiricus1990Pyrrhonism}
the author states that the logical criterium can be judged according to a frame of reference.
For our argument, as in \autocite{Santaca2016abf}, we define this concept
as Knowledge (or Facts); where knowledge is defined, as in \autocite{Steup2020epistemology}, as
a set of proposition known by an agent, such that: (i) knowledge requires belief,
(ii) knowledge require truth, (iii) knowledge must be \emph{properly justified}.
}
